---
title: "R Notebook"
output: 
  html_notebook: 
    number_sections: yes
---

# Decomposition

The matching function is

$$h_{j,t}=A_{j,t}\times v_{j,t}^{\alpha}\times u_{j,t}^{1-\alpha}.$$

The optimal allocation is

$$u_{j,t}^*=\frac{A_{j,t}^{1/\alpha}v_{j,t}}{\sum_{j'}A_{j',t}^{1/\alpha}v_{j',t}}u_{t},$$

and the job production is

$$h_{j,t}^*=A_{j,t}v_{j,t}^{\alpha}\times \frac{A_{j,t}^{1-\alpha/\alpha}v_{j,t}^{1-\alpha}}{\sum_{j'}A_{j',t}^{1/\alpha}v_{j',t}}u_{t}^{1-\alpha}.$$


$$=A_{j,t}^{1/\alpha}v_{j,t}\times \frac{1}{[\sum_{j'}A_{j',t}^{1/\alpha}v_{j',t}]^{1-\alpha}}u_{t}^{1-\alpha}$$

The aggregate production is

$$h_t^*=\sum h_{j,t}^*=\tilde{A}_t\times v_{t}^{\alpha}\times u_{t}^{1-\alpha}$$

where

$$\tilde A_{t}=[\sum_{j'}A_{j',t}^{1/\alpha}\times \frac{v_{j',t}}{v_t}]^{\alpha}.$$

The job finding rate can be decomposed as

$$\log\frac{p_t}{p_{t-12}}=\log m_t+\log h_t^* - \log m_{t-12} -\log h^*_{t-12}$$

$$=\underbrace{\log m_t - \log m_{t-12}}_{Mismatch}$$

$$+\underbrace{\log \tilde A_t-\log \tilde A_{t-12}}_{Efficiency}$$

$$+\underbrace{\alpha[\log v_t - \log v_{t-12}}_{Vacancy}]$$

$$-\underbrace{\alpha[\log u_t - \log u_{t-12}}_{Seeker}]$$

# Environment

```{r environment, message = FALSE}
library(readxl)
library(tidyverse)
library(lubridate)
```

# Data import

## Date label

- From March 2012 to March 2021

```{r}
year_month <- 
  c(rep(2012,10),
    rep(2013,12),
    rep(2014,12),
    rep(2015,12),
    rep(2016,12),
    rep(2017,12),
    rep(2018,12),
    rep(2019,12),
    rep(2020,12),
    rep(2021,3)
    ) %>%
  cbind(c(3:12,1,2))
```

## OCcupation  label

```{r grobal occupation}
occ <- c("Management",
         "Technical specialist",
         "Office",
         "Sales",
         "Service",
         "Security",
         "Agriculture, Forestry, and Fisheries",
         "Production process",
         "Driver",
         "Construction and Mining",
         "Others")
```

## Relevant range

```{r}
sel.raw <- c(5,6,19,27,31,40,41,42,54,60,66)

sel.col <- c(19:127)
```

### Full time

```{r full time occupation}
raw.new.vac <- 
  read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
             sheet = "第２１表ー８　 新規求人（パート除く常用）")
raw.vac <- 
  read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
             sheet = "第２１表ー９　有効求人（パート除く常用）")
raw.new.see <- 
  read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
             sheet = "第２１表ー１０　新規求職（パート除く常用）")
raw.see <- 
  read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
             sheet = "第２１表ー１１　有効求職（パート除く常用）")
raw.hir <- 
  read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
             sheet = "第２１表ー１２　就職件数（パート除く常用）")

raw <- 
  raw.new.vac[sel.raw,sel.col] %>%
  mutate(occ = occ)

name <- names(raw)[-ncol(raw)]

df <- 
  gather(raw,
         name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Vacancy"
         ) %>%
  ungroup

df <- 
  raw.new.see[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Seeker") %>%
  ungroup %>%
  rbind(df)

df <- 
  raw.hir[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Employment") %>%
  ungroup %>%
  rbind(df)

df <- 
  raw.see[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "Seeker") %>%
  ungroup %>%
  rbind(df)

df <- 
  raw.vac[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "Vacancy") %>%
  ungroup %>%
  rbind(df) %>%
  mutate(job_type = "Full-time")
```

### Part time

```{r part time occupation}
raw.new.vac <- read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
                      sheet = "第２１表ー１５　新規求人（常用的パート）")
raw.vac <- read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
                      sheet = "第２１表ー１６　有効求人（常用的パート）")
raw.new.see <- read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
                      sheet = "第２１表ー１７　新規求職（常用的パート）")
raw.see <- read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
                      sheet = "第２１表ー１８　有効求職（常用的パート）")
raw.hir <- read_excel("C:/Users/kawata/Dropbox/data/RPPERS/第21表.xlsx",
                      sheet = "第２１表ー１９　就職件数（常用的パート）")

df <- 
  raw.new.vac[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Vacancy"
         ) %>%
  ungroup %>%
  mutate(job_type = "Part-time") %>%
  rbind(df)

df <- 
  raw.new.see[sel.raw,sel.col] %>%
  mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Seeker"
         ) %>%
  ungroup %>%
  mutate(job_type = "Part-time") %>%
  rbind(df)

df <- 
  raw.hir[sel.raw,sel.col] %>%
   mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "New Employment"
         ) %>%
  ungroup %>%
  mutate(job_type = "Part-time") %>%
  rbind(df)

df <- 
  raw.vac[sel.raw,sel.col] %>%
   mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "Vacancy"
         ) %>%
  ungroup %>%
  mutate(job_type = "Part-time") %>%
  rbind(df)

df <- 
  raw.see[sel.raw,sel.col] %>%
   mutate(occ = occ) %>%
  gather(name,
         key = "date",
         value = "n") %>%
  group_by(occ) %>%
  mutate(year = year_month[,1],
         month = year_month[,2],
         type = "Seeker"
         ) %>%
  ungroup %>%
  mutate(job_type = "Part-time") %>%
  rbind(df) %>%
  mutate(n = as.numeric(n))

```

# Estimation

Suppose a matching function as

$$p_{jt} = A_{jt}\theta_{jt}^{\eta}$$

```{r estimation occupation}
eta.full <- 
  df %>%
  spread(key = type,
         value = n) %>%
  mutate(p = `New Employment`/Seeker,
         t = Vacancy/Seeker) %>%
  filter(job_type == "Full-time") %>%
  filter(occ != "Others") %>%
  lm(log(p) ~ log(t) + factor(occ) + factor(month) + factor(year),
     data =.) %>%
  coef %>%
  .[2]

eta.part <- 
  df %>%
  spread(key = type,
         value = n) %>%
  mutate(p = `New Employment`/Seeker,
         t = Vacancy/Seeker) %>%
  filter(job_type == "Part-time") %>%
  filter(occ != "Others") %>%
  lm(log(p) ~ log(t) + factor(occ) + factor(month) + factor(year),
     data =.) %>%
  coef %>%
  .[2]

result <-
  df %>%
  spread(key = type,
         value = n) %>%
  filter(occ != "Others") %>%
  mutate(p = `New Employment`/Seeker,
         t = Vacancy/Seeker,
         eta = if_else(job_type == "Full-time",
                       eta.full,
                       eta.part
                       ),
         A = p/(t^eta),
         weight = (A^(1/eta))*Vacancy,
         date = make_date(year,month)
         )  %>%
  group_by(job_type,
           date) %>%
  mutate(weight = weight/sum(weight),
         Optimal.Seeker = weight*sum(Seeker),
         Optimal.Hir = A*(Vacancy^(eta))*(Optimal.Seeker^(1-eta)),
         Optimal.Agg.Hir = sum(Optimal.Hir),
         Agg.Hir = sum(`New Employment`),
         Agg.Mismatch = (Optimal.Agg.Hir - Agg.Hir)/Agg.Hir) %>%
  ungroup
```

# Visualization

## Aggreagte

```{r}
fig <-
  df %>%
  mutate(date = make_date(year,month)) %>%
  filter(type == "Seeker" |
           type == "Vacancy" |
           type == "New Employment") %>%
  group_by(type,
           date,
           job_type) %>%
  mutate(n = sum(n)) %>%
  ungroup %>%
  distinct(n,type,job_type,date) %>%
  ggplot(aes(x = date,
             y = n)
         ) +
  geom_line() +
  facet_grid(type~job_type,
             scale = "free")

fig
```


## Full-time/Seeker

```{r}
fig <-
  df %>%
  mutate(date = make_date(year,month)) %>%
  filter(type == "Seeker") %>%
  filter(job_type == "Full-time") %>%
  group_by(occ,
           date,
           job_type) %>%
  mutate(n = sum(n)) %>%
  ungroup %>%
  distinct(n,occ,job_type,date) %>%
  ggplot(aes(x = date,
             y = n)
         ) +
  geom_line() +
  facet_wrap(~ occ,
             scale = "free",
             ncol = 3)

fig
```

## Mismatch

```{r}
fig <-
  result %>%
  distinct(Agg.Mismatch,
           job_type,
           date) %>%
  ggplot(aes(x = date,
             y = Agg.Mismatch)
         ) +
  geom_line() +
  facet_wrap(~job_type,
             scale = "free",
             ncol = 1) +
  theme_bw() +
  ylab("Mismatch Index")

fig

ggsave("figure/occ_mismatch.png",
       plot = fig,
       dpi = "retina")
```

